### 2011-06-23 docs/analysis/analysis.tex
fix list
move some particle stuff from architecture.  Some updates.

\section{The {\tt data\_processing} Routines}

The {\tt fParallel/data\_processing/} directory contains a large
number of Fortran-based analysis routines for BoxLib datasets.  Many
of these can be used with both MAESTRO and the compressible
astrophysics code, Castro.

@@

  Laterally average each of the variables in a plotfile (works for
  both 2-d and 3-d).  This is written with MAESTRO
  plane-parallel geometry plotfiles in mind, and the averaging is done
  over the coordinate direction(s) perpendicular to gravity.

@@

A well-commented example processing routine is provided in {\tt
  data\_processing/tutorial} as {\tt fspeciesmass2d.f90}.  This
routine simply computes the total mass of a particular species on the
entire domain for a 2-d dataset.  It is written to understand a
multilevel (AMR) dataset, and only considers the finest-available data
at any physical location in the computational domain.

@@

>>>>

\section{The {\tt data\_processing} Routines}
\label{sec:analysis}

The {\tt fParallel/data\_processing/} directory contains a large
number of Fortran-based analysis routines for BoxLib datasets.  Many
of these can be used with both \maestro\ and the compressible
astrophysics code, \castro.

@@

  Laterally average each of the variables in a plotfile (works for
  both 2-d and 3-d).  This is written with \maestro\
  plane-parallel geometry plotfiles in mind, and the averaging is done
  over the coordinate direction(s) perpendicular to gravity.

@@

The routine {\tt fspeciesmass2d.f90} in {\tt
  data\_processing/tutorial} serves as a well-commented example of how
to work with \maestro\ plotfile data.  This routine simply computes
the total mass of a particular species on the entire domain for a 2-d
dataset.  It is written to understand a multilevel (AMR) dataset, and
only considers the finest-available data at any physical location in
the computational domain.

@@

\subsection{Particle routines}

\label{analysis:sec:particles}

The {\tt parseparticles.py} routine in the {\tt python/} subdirectory
can read in \maestro\ particle files containing particle histories
(usually named {\tt timestamp\_??}).  See the discussion in \S~\ref{arch:sec:particles} for details on initialization.  The driver {\tt
  test\_parseparticles.py} shows shows how to use this module to plot
particle histories.

As a concrete example, running {\tt test2} with particles enabled
will seed particles in the initial hotspot.  To plot the results,
first set your {\tt PYTHONPATH} environment variable to point to the
{\tt fParallel/data\_processing/python/} directory, for example:
\begin{verbatim}
export PYTHONPATH="/home/username/development/MAESTRO/fParallel/data_processing/python"
\end{verbatim}
This will allow python to see the {\tt parseparticles.py} routine.
For the {\tt test2} problem, the {\tt plotparticles.py} routine shows
how to plot the particle histories and make an animation of the
particles colored by the ash mass fraction.  This script is run as:
\begin{verbatim}
./plotparticles.py timestamp_*
\end{verbatim}

Note, these python routines require the NumPy and matplotlib packages.
On a Fedora Linux system, the necessary routines can be installed via:
\begin{verbatim}
yum install python-matplotlib lyx-fonts stix-fonts
\end{verbatim}
